### 2022-02-23 README.Rmd
improved ggplot2 scales: todo binned scales and docs
ready

The **cols4all** is an R package in development for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. This package contains palettes from several popular color palette series, such as Color Brewer, Viridis, and Kovesi, but also the lesser known [palettes from Paul Tol](https://personal.sron.nl/~pault/). Own palettes series can be added as well. Color palettes are well organized. Currently we support three types: *categorical* (qualitative) palettes, *sequential* palettes, and *diverging* palettes. In the near future, more palette types will be added, namely *cyclic*, *bivariate*, and *hierarchical*.

@@

**cols4all** will be available on CRAN soon! Until then it can be installed using:

@@

```{r, eval=FALSE}
library(cols4all)
c4a_gui()
```

@@

Selecting a palette is easy. Palette names are in the format <series>.<palette_name>. So all letters are in small caps, and underscores are used to separate words.

@@

The foundation of this package is another R package: [**colorspace**](https://colorspace.r-forge.r-project.org/). We use this package to analyse colors. For this purpose, we also use [**colorblindcheck**](https://github.com/Nowosad/colorblindcheck).

There are a few features that distinguishes **cols4all** from other (great) color palette packages, in particular [**pals**](https://kwstat.github.io/pals/) and [**paletteer**](https://github.com/EmilHvitfeldt/paletteer):

@@

* With the gui (see below), a user is able to analyse characteristics of color palettes, such as color-blind-friendliness, harmony, and the presence of intense colors.

@@

There will be native support for **ggplot** and **tmap** (as of the upcoming version 4)

>>>>

The **cols4all** is an R package in development for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series: [Color Brewer](https://colorbrewer2.org), [Viridis](http://bids.github.io/colormap/), [Kovesi](https://colorcet.com/), [Paul Tol](https://personal.sron.nl/~pault/), [Scico](https://www.fabiocrameri.ch/colourmaps/), [Carto](https://carto.com/carto-colors/), [Tableau](https://www.tableau.com/about/blog/2016/7/colors-upgrade-tableau-10-56782) and [Wes Anderson](https://github.com/karthik/wesanderson). Own palettes series can be added as well. Color palettes are well organized. Currently we support three types: *categorical* (qualitative) palettes, *sequential* palettes, and *diverging* palettes. In the near future, more palette types will be added, namely *cyclic*, *bivariate*, and *hierarchical*.

@@

**cols4all** will be available on CRAN soon. Until then it can be installed using:

@@

```{r, eval=FALSE}
library(cols4all)
# For the GUI, shiny, shinyjs and kableExtra are required
# install.packages(c("shiny", "shinyjs", "kableExtra"))
c4a_gui()
```

@@

Selecting a palette is easy:

@@

The foundation of this package is another R package: [**colorspace**](https://colorspace.r-forge.r-project.org/). We use this package to analyse colors. For this purpose and specifically for color blind friendliness checks, we also use [**colorblindcheck**](https://github.com/Nowosad/colorblindcheck).

There are a few other pacakges with a large collection of color palettes, in particular [**pals**](https://kwstat.github.io/pals/) and [**paletteer**](https://github.com/EmilHvitfeldt/paletteer). There are a few features that distinguishes **cols4all** from those packages:

@@

* The GUI enables users to analyse characteristics of color palettes, such as color-blind-friendliness, harmony, and the presence of intense colors.

* There is native support for **ggplot2** and **tmap** (as of the upcoming version 4).

@@

## Feedback welcome!

* Is everything working as expected?

* Do you miss certain palettes or series?

* Do you have ideas for improvement how to measure palette properties?

Let us know! (via github issues)
